---
title: "R Notebook"
output: html_notebook
---

ike_date <- lubridate::ymd_hms("2008-09-13 12:00:00", tz = "GMT")
ike_obs <- stormObservation("Ike",ike_date)
first_row <- ike_obs[1,]

## Load libraries
Load the `stormplot` package
```{r}
devtools::load_all()
```

## Get a storm observation
Storm observations include info on windspeed at different points in time for a specified storm.  The data covers all storms in the Atlantic basin from 1988–2015 (extended best tracks).
```{r}
ike_date <- lubridate::ymd_hms("2008-09-13 12:00:00", tz = "GMT")
ike_obs <- stormObservation("Ike",ike_date)
first_row <- ike_obs[1,]
first_row
```

## Plot a storm observation (without map)
We can use the `geom_hurricane` method to plot a 2-d visual representation of the hurricane's wind strength
```{r}
katrina_date <- lubridate::ymd_hms("2005-08-29 12:00:00", tz = "GMT")
katrina <- stormObservation("Katrina", katrina_date)

# demonstrates use of geom_hurricane
ggplot(data = katrina) +
  geom_hurricane(aes(x = longitude, y = latitude,
                     r_ne = ne, r_se = se, r_nw = nw, r_sw = sw,
                     fill = wind_speed, color = wind_speed)) +
  scale_color_manual(name = "Wind speed (kts)",
                     values = c("red", "orange", "yellow")) +
  scale_fill_manual(name = "Wind speed (kts)",
                    values = c("red", "orange", "yellow")) 

```

## Plot hurricane on map
Mapping an observation is simplified with `mapObservation`
```{r}
mapObservation(ike_obs)
```
